---
title: "R01-FBS: Task EF x Risk Status Paper"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
header-includes:
- \usepackage{fullpage}
- \usepackage{graphicx}
- \usepackage{subcaption}
- \usepackage{float}
- \usepackage{placeins}
- \usepackage{caption}
- \usepackage{mathtools}
# - \usepackage{multirow}
- \usepackage{amssymb}
- \usepackage{amsmath}
- \usepackage{bigstrut}
- \usepackage{geometry}
# - \usepackage{pdflscape}
- \setlength{\parskip}{1em}
geometry: margin=1.3cm
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE, tidy.opts = list(comment = FALSE), echo = TRUE, fig.width=6, fig.height=4, fig.path='figs/', fig.pos='H', echo=FALSE, cache = FALSE, warning=FALSE, message=FALSE, comment = NA)
```

<!-- load startup file and any extra packages -->
```{r load, echo=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(stats)
library(haven)
library(psycho)
library(reshape2)
library(gtsummary)
theme_gtsummary_compact()

library(car)
library(emmeans)

library(lme4)
library(lmerTest)
library(ggplot2)
library(ggpubr)
library(ggsignif)


source('functions.R')
```

```{r load_scripts, echo=FALSE, results='asis'}
source('setup.R')
source('tables.R')
source('analyses.R')
source('figures.R')
```

\clearpage

# Participant Characteristics (Demographics Database)

```{r demo_tab, echo=FALSE, results='asis'}
  as_kable_extra(partab_risk, caption = 'Demographic Characteristics', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

\FloatBarrier
\clearpage

## income
```{r demo_incom, echo=FALSE}
income_chi
```

## mom education
```{r demo_momed, echo=FALSE}
momed_fisher
```

## bmi percentile
```{r demo_bmi, echo=FALSE}
bmi_t
```

## percent body fat
```{r demo_pbf, echo=FALSE}
pbf_t
```


# Effect of Risk Status

## Go-NoGo

```{r gng_tab, echo=FALSE, results='asis'}
as_kable_extra(gngtab, caption = 'Go-NoGo Performance Summary', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```
\

\FloatBarrier

### Percent False Alarms

\FloatBarrier

```{r gng_fa_avnova_momrisk, echo=FALSE, results='asis'}
kable(round(gng_fa_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo Percent False Alarms', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r gng_fa_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 4}
gng_fa_plot
```

\FloatBarrier

There was a significant effect of familial obesity risk such that children with high risk had a false alarm percentage that was 7.8 points higher than those with low risk. SES, age, and sex were not associated with false alarm percentage.

\FloatBarrier
\clearpage

### Percent Hits

```{r gng_hits_risk_mod, echo=FALSE, results='asis'}
kable(round(gng_hits_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Percent Hits', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

Correct responses to go stimuli did not differ by risk status, age, sex, or SES.

\FloatBarrier

### Go Reaction Time

```{r gng_hits_rt_mod, echo=FALSE, results='asis'}
kable(round(gng_rt_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Go Reaction Time', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

Correct responses to go stimuli did not differ by risk status, sex, or SES. However, older children responded more quickly than younger children.

\FloatBarrier

### d'

```{r gng_dprime_risk_mod, echo=FALSE, results='asis'}
kable(round(gng_dprime_sum$coefficients, digits = 3), "latex",  digits = 3, caption = "Go-NoGo - d'", booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

Sensitivity indexed by d' did not differ by risk status, age, sex, or SES.

\FloatBarrier
\clearpage

## Stop-Signal Task

```{r sst_tab, echo=FALSE, results='asis'}
as_kable_extra(sst_all_tab, caption = 'Stop-Signal Task Performance Summary: Risk Status across all trials', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```
\
\FloatBarrier


```{r sstED_tab, echo=FALSE, results='asis'}
as_kable_extra(sstED_tab, caption = 'Stop-Signal Task Performance Summary: Risk Status by Energy Density Condition', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```
\
\FloatBarrier

```{r sstPS_tab, echo=FALSE, results='asis'}
as_kable_extra(sstPS_tab, caption = 'Stop-Signal Task Performance Summary: Risk Status by Portion Size Condition', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

\
\FloatBarrier
\clearpage

### Stop Signal Reaction Time

#### Design

\FloatBarrier

```{r sst_ssrtdesign_mod, echo=FALSE, results='asis'}
kable(round(sst_ssrtdesign_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - ED x PS', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrtdesign_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrtdesign_plot
```

No effect of energy density, portion size, or interaction.

\clearpage

#### Overall

\FloatBarrier

```{r sst_ssrt_risk_mod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrt_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrt_plot
```

Across all trials, there was a significant effect of familial obesity risk on stop-signal reaction time (SSRT). SSRT was slower (worse) in children with high risk compared to those with low risk. Additionally, older children were showed faster SSRT. There was no association with sex or SES.

```{r sst_ssrt_risk_mod_posthoc}
emmeans(sst_ssrt_model, specs = pairwise ~ risk_status_mom)
test(emtrends(sst_ssrt_model, ~age_yr, var = 'age_yr'))
```

\FloatBarrier
\clearpage

#### Energy Density Trials

\FloatBarrier

```{r sst_ssrt_risk_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - ED x Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrtED_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrtED_plot
```

SSRT was slower (worse) in children with high risk compared to those with low risk. 

```{r sst_ssrt_risk_EDmod_posthoc}
emmeans(sst_ssrt_EDmodel, specs = pairwise ~ risk_status_mom)
emmeans(sst_ssrt_EDmodel, specs = pairwise ~ ED)

```
\FloatBarrier
\clearpage

#### Portion Size Trials

\FloatBarrier

```{r sst_ssrt_risk_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - PS x Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrtPS_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrtPS_plot
```

SSRT was slower (worse) in children with high risk compared to those with low risk. 

```{r sst_ssrt_risk_PSmod_posthoc}
emmeans(sst_ssrt_PSmodel, specs = pairwise ~ risk_status_mom)
emmeans(sst_ssrt_PSmodel, specs = pairwise ~ PS)

```
\FloatBarrier
\clearpage

### Stop Signal Delay

#### Design

\FloatBarrier

```{r sst_ssddesign_mod, echo=FALSE, results='asis'}
kable(round(sst_ssddesign_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - ED x PS', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssddesign_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssddesign_plot
```

No effect of portion size or interaction. A trend for an effect of  energy density such that there was a lower SSD (worse) for high ED compared to low ED blocks. 

```{r sst_ssddesign_mod_posthoc, echo=FALSE}
emmeans(sstdesign_ssd_model, specs = pairwise ~ ED)
```


\FloatBarrier

```{r sst_ssddesignED_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssddesignED_plot
```

\FloatBarrier
\clearpage

#### All Trials


```{r sst_ssd_risk_mod, echo=FALSE, results='asis'}
kable(round(sst_ssd_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssd_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssd_plot
```

Main effect of risk status such that children at high risk have shorter stop signal delays (worse) than children at low risk. 

```{r sst_ssd_risk_mod_posthoc, echo=FALSE}
emmeans(sst_ssd_model, specs = pairwise ~ risk_status_mom)
```

\FloatBarrier
\clearpage

#### Energy Density Trials

\FloatBarrier

```{r sst_ssd_risk_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Risk Status x ED', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssdED_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssdED_plot
```

Main effect of risk status such that children at high risk have shorter stop signal delays (worse) than children at low risk. Boys also have shorter stop signal delays than girls.

```{r sst_ssd_risk_EDmod_posthoc, echo=FALSE}
emmeans(sst_ssd_EDmodel, specs = pairwise ~ risk_status_mom)
emmeans(sst_ssd_EDmodel, specs = pairwise ~ ED)
```

\FloatBarrier
\clearpage

#### Portion Size Trials

\FloatBarrier

```{r sst_ssd_risk_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Risk Status x PS', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssdPS_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssdPS_plot
```

Main effect of risk status such that children at high risk have shorter stop signal delays (worse) than children at low risk. Boys also have shorter stop signal delays than girls.

```{r sst_ssd_risk_PSmod_posthoc, echo=FALSE}
emmeans(sst_ssd_PSmodel, specs = pairwise ~ risk_status_mom)
emmeans(sst_ssd_PSmodel, specs = pairwise ~ PS)
emmeans(sst_ssd_PSmodel, specs = pairwise ~ sex)
```

\FloatBarrier
\clearpage

## N-back

```{r nback_risk_tab, echo=FALSE, results='asis'}
as_kable_extra(nbacktab_all, caption = 'Nback Performance Summary',  format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```
\
\FloatBarrier
\clearpage

### Ballanced Accuracy

\FloatBarrier

```{r nback_balacc_risk_mod, echo=FALSE, results='asis'}
kable(round(nback_balacc_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Risk Status x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

```{r nback_balacc_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
nback_balacc_plot
```

Interaction between risk and load shows that children at high familial risk for obesity perform worse at the highest working memory load compared to children at low risk.

```{r nback_balacc_risk_mod_posthoc, echo=FALSE}
emmeans(nback_balacc_mod, specs = pairwise ~ block, adjust = 'none')
emmeans(nback_balacc_mod, specs = pairwise ~ risk_status_mom, adjust = 'none')

emmeans(nback_balacc_mod, specs = pairwise ~ block:risk_status_mom, adjust = 'none')
```

\FloatBarrier
\clearpage

### d'

\FloatBarrier

```{r nback_dprime_risk_mod, echo=FALSE, results='asis'}
kable(round(nback_dprime_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Risk Status x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

```{r nback_dprime_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
nback_drime_plot
```

Interaction between risk and load shows that children at high familial risk for obesity perform worse at the highest working memory load compared to children at low risk.

```{r nback_dprime_risk_mod_posthoc, echo=FALSE}
emmeans(nback_dprime_mod, specs = pairwise ~ block:risk_status_mom, adjust = 'none')
emmeans(nback_dprime_mod, specs = pairwise ~ block, adjust = 'none')
```

\FloatBarrier
\clearpage

# Effect of Total Body Fat Percentage

## Go-NoGo

### Percent False Alarms

\FloatBarrier

```{r gng_fa_bfp_mod, echo=FALSE, results='asis'}
kable(round(gng_fa_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo Percent False Alarms - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

### Percent Hits

```{r gng_hits_bfp_mod, echo=FALSE, results='asis'}
kable(round(gng_hits_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Percent Hits - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

Correct responses to go stimuli did not differ by risk status, age, sex, or SES.

\FloatBarrier

### Go Reaction Time

```{r gng_hits_rt_bfp_mod, echo=FALSE, results='asis'}
kable(round(gng_rt_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo - Go Reaction Time', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier

### d'

```{r gng_dprime_bfp_mod, echo=FALSE, results='asis'}
kable(round(gng_dprime_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = "Go-NoGo - d'", booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


\FloatBarrier
\clearpage

## Stop-Signal Task

### Stop Signal Reaction Time


#### Overall

\FloatBarrier

```{r sst_ssrt_bfp_mod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

### Energy Density Trials

\FloatBarrier

```{r sst_ssrt_bfp_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - ED x Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
```{r sst_ssrt_bfp_EDmod_posthoc, echo=FALSE}
test(emtrends(sst_ssrt_bfp_EDmod, ~ bfp_center, var = 'bfp_center'))
emmeans(sst_ssrt_bfp_EDmod, specs = pairwise ~ ED)
```

\FloatBarrier

### Portion Size Trials

\FloatBarrier

```{r sst_ssrt_bfp_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - PS x Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
```{r sst_ssrt_bfp_PSmod_posthoc, echo=FALSE}
test(emtrends(sst_ssrt_bfp_PSmod, ~ bfp_center, var = 'bfp_center'))
emmeans(sst_ssrt_bfp_PSmod, specs = pairwise ~ PS)
```
\FloatBarrier
\clearpage

### Stop Signal Delay

#### Overall

\FloatBarrier

```{r sst_ssd_bfp_mod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Body Fat Percentage', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssd_bfp_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssd_bfp_plot
```

There was an effect of of body fat percentage such that higher body fat percentage was associated with shorter stop signal delays (worse). 

\FloatBarrier
\clearpage

#### Energy Density Trials

\FloatBarrier
\clearpage

```{r sst_ssd_bfp_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Body Fat Percentage x ED', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
```{r sst_ssd_bfp_EDmod_posthoc, echo=FALSE}
test(emtrends(sst_ssd_bfp_EDmod, ~ bfp_center, var = 'bfp_center'))
emmeans(sst_ssd_bfp_EDmod, specs = pairwise ~ ED)
```
\FloatBarrier

```{r sst_ssd_bfp_EDfig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssd_bfp_EDplot
```

There was no interaction between energy density and body fat percentage. There was, however, an effect of energy density and an effect of body fat percentage. Children had shorter stop signal delays (worse) during high energy dense blocks compared to low energy density blocks. Higher body fat percentage was associated with shorter stop signal delays (worse). 


\FloatBarrier
\clearpage

#### Portion Size Trials

\FloatBarrier

```{r sst_ssd_bfp_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Body Fat Percentage x PS', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
```{r sst_ssd_bfp_PSmod_posthoc, echo=FALSE}
test(emtrends(sst_ssd_bfp_PSmod, ~ bfp_center, var = 'bfp_center'))
emmeans(sst_ssd_bfp_PSmod, specs = pairwise ~ PS)
```

\FloatBarrier
\
 
```{r sst_ssd_bfp_PSfig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssd_bfp_PSplot
```

There was no interaction between portion size and body fat percentage. There was, however, an effect of portion size and an effect of body fat percentage. Children had longer stop signal delays (better) during blocks where 80% of stop trials were large portion compared to small portion. Higher body fat percentage was associated with shorter stop signal delays (worse). 

\FloatBarrier
\clearpage

## N-back

### Ballanced Accuracy

\FloatBarrier

```{r nback_balacc_bfp_mod, echo=FALSE, results='asis'}
kable(round(nback_balacc_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Body Fat Percentage x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

```{r nback_balacc_bfp_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
nback_balacc_bfp_plot
```

Interaction between total body fat percentage and load shows that higher body fat percentages are associated with worse working memory at the highest load (2-back)

```{r nback_balacc_bfp_mod_posthoc, echo=FALSE}
emmeans(nback_balacc_bfp_mod, specs = pairwise ~ block)
test(emtrends(nback_balacc_bfp_mod, ~ block:bfp_center, var = 'bfp_center'))
```

\FloatBarrier
\clearpage

### d'

\FloatBarrier

```{r nback_dprime_bfp_mod, echo=FALSE, results='asis'}
kable(round(nback_dprime_bfp_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Body Fat Percentage x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
```{r nback_dprime_bfp_mod_posthoc, echo=FALSE}
emmeans(nback_dprime_bfp_mod, specs = pairwise ~ block)
test(emtrends(nback_dprime_bfp_mod, ~ bfp_center, var = 'bfp_center'))
```
\FloatBarrier
\clearpage

# Exploratory Analyses: relative impact of risk and body fat percentage

## Go-NoGo

### Percent False Alarms

\FloatBarrier

```{r gng_fa_bfp_risk_mod, echo=FALSE, results='asis'}
kable(round(gng_fa_bfp_risk_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Go-NoGo Percent False Alarms - Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier
\clearpage

## Stop-Signal Task

### Stop Signal Reaction Time


#### Overall

\FloatBarrier

```{r sst_ssrt_bfp_risk_mod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_risk_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

### Energy Density Trials

\FloatBarrier

```{r sst_ssrt_bfp_risk_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_risk_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - ED  + Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier

### Portion Size Trials

\FloatBarrier

```{r sst_ssrt_bfp_risk_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssrt_bfp_risk_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - PS + Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier
\clearpage

### Stop Signal Delay

#### Overall

\FloatBarrier

```{r sst_ssd_bfp_risk_mod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_risk_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier
\clearpage

#### Energy Density Trials

\FloatBarrier
\clearpage

```{r sst_ssd_bfp_risk_EDmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_risk_EDsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - ED + Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```


#### Portion Size Trials

\FloatBarrier

```{r sst_ssd_bfp_risk_PSmod, echo=FALSE, results='asis'}
kable(round(sst_ssd_bfp_risk_PSsum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - PS + Body Fat Percentage + Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\FloatBarrier
\clearpage

## N-back

### Ballanced Accuracy

\FloatBarrier

```{r nback_balacc_bfp_risk_mod, echo=FALSE, results='asis'}
kable(round(nback_balacc_bfp_risk_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Body Fat Percentage x Load + Risk Status x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\

```{r nback_balacc_bfp_risk_mod_posthoc, echo=FALSE}
emmeans(nback_balacc_bfp_risk_mod, specs = pairwise ~ risk_status_mom, adjust = 'none')
emmeans(nback_balacc_bfp_risk_mod, specs = pairwise ~ block:risk_status_mom, adjust = 'none')
test(emtrends(nback_balacc_bfp_risk_mod, ~ bfp_center, var = 'bfp_center'))
```
\FloatBarrier

### d'

\FloatBarrier

```{r nback_dprime_bfp_risk_mod, echo=FALSE, results='asis'}
kable(round(nback_dprime_bfp_risk_sum$coefficients, digits = 3), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Body Fat Percentage x Load + Risk Status x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```
\
```{r nback_dprime_bfp_risk_mod_posthoc, echo=FALSE}
emmeans(nback_dprime_bfp_risk_mod, specs = pairwise ~ risk_status_mom, adjust = 'none')
emmeans(nback_dprime_bfp_risk_mod, specs = pairwise ~ block:risk_status_mom, adjust = 'none')
test(emtrends(nback_dprime_bfp_risk_mod, ~ bfp_center, var = 'bfp_center'))
```
\FloatBarrier
\clearpage
