---
title: "R01-FBS: Task EF x Risk Status Paper"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
header-includes:
- \usepackage{fullpage}
- \usepackage{graphicx}
- \usepackage{subcaption}
- \usepackage{float}
- \usepackage{placeins}
- \usepackage{caption}
- \usepackage{mathtools}
# - \usepackage{multirow}
- \usepackage{amssymb}
- \usepackage{amsmath}
- \usepackage{bigstrut}
- \usepackage{geometry}
# - \usepackage{pdflscape}
- \setlength{\parskip}{1em}
geometry: margin=1.3cm
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE, tidy.opts = list(comment = FALSE), echo = TRUE, fig.width=6, fig.height=4, fig.path='figs/', fig.pos='H', echo=FALSE, cache = FALSE, warning=FALSE, message=FALSE, comment = NA)
```

<!-- load startup file and any extra packages -->
```{r load, echo=FALSE, include=FALSE}
library(knitr)
library(kableExtra)
library(stats)
library(haven)
library(psycho)
library(reshape2)
library(gtsummary)
theme_gtsummary_compact()

library(car)
library(emmeans)

library(lme4)
library(lmerTest)
library(ggplot2)
library(ggpubr)
library(ggsignif)


source('functions.R')
```

```{r load_scripts, echo=FALSE, results='asis'}
source('setup.R')
source('tables.R')
source('analyses.R')
source('figures.R')
```

\clearpage

# Participant Characteristics (Demographics Database)

```{r demo_tab, echo=FALSE, results='asis'}
as_kable_extra(partab_risk, caption = 'Demographic Characteristics', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

\FloatBarrier
\clearpage

## Go-NoGo

```{r gng_tab, echo=FALSE, results='asis'}
as_kable_extra(gngtab, caption = 'Go-NoGo Performance Summary', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

\FloatBarrier

### Percent False Alarms

\FloatBarrier

```{r gng_fa_avnova_momrisk, echo=FALSE, results='asis'}
kable(anova2dataframe(gng_fa_anova), "latex",  digits = 3, caption = 'Go-NoGo Percent False Alarms', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r gng_fa_plot, echo=FALSE, include = TRUE, fig.height = 4, fig.width = 4}
gng_fa_plot
```

\FloatBarrier

There was a significant effect of familial obesity risk such that children with high risk had a false alarm percentage that was 7.8 points higher than those with low risk. SES, age, and sex were not associated with false alarm percentage.

\FloatBarrier
\clearpage

### Percent Hits

```{r gng_hits_risk_anova, echo=FALSE, results='asis'}
kable(anova2dataframe(gng_hits_anova), "latex",  digits = 3, caption = 'Go-NoGo - Percent Hits', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

Correct responses to go stimuli did not differ by risk status, age, sex, or SES.

\FloatBarrier

### Go Reaction Time

```{r gng_hits_rt_anova, echo=FALSE, results='asis'}
kable(anova2dataframe(gng_rt_anova), "latex",  digits = 3, caption = 'Go-NoGo - Go Reaction Time', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

Correct responses to go stimuli did not differ by risk status, sex, or SES. However, older children responded more quickly than younger children.

\FloatBarrier

### d'

```{r gng_dprime_risk_anova, echo=FALSE, results='asis'}
kable(anova2dataframe(gng_dprime_anova), "latex",  digits = 3, caption = "Go-NoGo - d'", booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

Sensitivity indexed by d' did not differ by risk status, age, sex, or SES.

\FloatBarrier
\clearpage

## Stop-Signal Task

```{r sstED_tab, echo=FALSE, results='asis'}
as_kable_extra(sstED_tab, caption = 'Stop-Signal Task Performance Summary: Risk Status by Energy Density Condition', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

```{r sstPS_tab, echo=FALSE, results='asis'}
as_kable_extra(sstPS_tab, caption = 'Stop-Signal Task Performance Summary: Risk Status by Portion Size Condition', format = "latex", booktabs = TRUE, longtable = FALSE) %>%
  kableExtra::kable_styling(latex_options = "HOLD_position",  full_width = FALSE)
```

\FloatBarrier
\clearpage

### Stop Signal Reaction Time

#### Design

\FloatBarrier

```{r sst_ssrtdesign_anova, echo=FALSE, results='asis'}
kable(anova2dataframe(sst_ssrtdesign_anova), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - ED x PS', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrtdesign_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrtdesign_plot
```

No effect of energy density, portion size, or interaction.

\clearpage

#### Overall

\FloatBarrier

```{r sst_ssrt_risk_anova, echo=FALSE, results='asis'}
kable(anova2dataframe(sst_ssrt_anova), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrt_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrt_plot
```

Across all trials, there was a significant effect of familial obesity risk on stop-signal reaction time (SSRT). SSRT was slower (worse) in children with high risk compared to those with low risk. Additionally, older children were showed faster SSRT. There was no association with sex or SES.

```{r sst_ssrt_risk_anova_posthoc}
emmeans(sst_ssrt_model, specs = pairwise ~ risk_status_mom)
test(emtrends(sst_ssrt_model, ~age_yr, var = 'age_yr'))
```

\FloatBarrier
\clearpage

#### Energy Density Trials

\FloatBarrier

```{r sst_ssrt_risk_EDanova, echo=FALSE, results='asis'}
kable(anova2dataframe(sst_ssrt_EDanova), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - ED x Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrtED_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrtED_plot
```

SSRT was slower (worse) in children with high risk compared to those with low risk. 

```{r sst_ssrt_risk_EDanova_posthoc}
emmeans(sst_ssrt_EDmodel, specs = pairwise ~ risk_status_mom)
```
\FloatBarrier
\clearpage

#### Portion Size Trials

\FloatBarrier

```{r sst_ssrt_risk_PSanova, echo=FALSE, results='asis'}
kable(anova2dataframe(sst_ssrt_PSanova), "latex",  digits = 3, caption = 'Stop-Signal Task SSRT - PS x Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssrtPS_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssrtPS_plot
```

SSRT was slower (worse) in children with high risk compared to those with low risk. 

```{r sst_ssrt_risk_PSanova_posthoc}
emmeans(sst_ssrt_PSmodel, specs = pairwise ~ risk_status_mom)
```
\FloatBarrier
\clearpage

### Stop Signal Delay

#### Design

\FloatBarrier

```{r sst_ssddesign_anova, echo=FALSE, results='asis'}
kable(anova2dataframe(sst_ssddesign_anova), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - ED x PS', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssddesign_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssddesign_plot
```

No effect of portion size or interaction. A trend for an effect of  energy density such that there was a lower SSD (worse) for high ED compared to low ED blocks. 

```{r sst_ssddesign_anova_posthoc, echo=FALSE}
emmeans(sstdesign_ssd_model, specs = pairwise ~ ED)
```


\FloatBarrier

```{r sst_ssddesignED_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssddesignED_plot
```

\FloatBarrier
\clearpage

#### All Trials


```{r sst_ssd_risk_anova, echo=FALSE, results='asis'}
kable(anova2dataframe(sst_ssd_anova), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Risk Status', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssd_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssd_plot
```

Main effect of risk status such that children at high risk have shorter stop signal delays (worse) than children at low risk. 

```{r sst_ssd_risk_anova_posthoc, echo=FALSE}
emmeans(sst_ssd_model, specs = pairwise ~ risk_status_mom)
```

\FloatBarrier
\clearpage

#### Energy Density Trials

\FloatBarrier

```{r sst_ssd_risk_EDanova, echo=FALSE, results='asis'}
kable(anova2dataframe(sst_ssd_EDanova), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Risk Status x ED', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssdED_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssdED_plot
```

Main effect of risk status such that children at high risk have shorter stop signal delays (worse) than children at low risk. Boys also have shorter stop signal delays than girls.

```{r sst_ssd_risk_EDanova_posthoc, echo=FALSE}
emmeans(sst_ssd_EDmodel, specs = pairwise ~ risk_status_mom)
emmeans(sst_ssd_EDmodel, specs = pairwise ~ sex)
```

\FloatBarrier
\clearpage

#### Portion Size Trials

\FloatBarrier

```{r sst_ssd_risk_PSanova, echo=FALSE, results='asis'}
kable(anova2dataframe(sst_ssd_PSanova), "latex",  digits = 3, caption = 'Stop-Signal Task SSD - Risk Status x PS', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

\

```{r sst_ssdPS_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
sst_ssdPS_plot
```

Main effect of risk status such that children at high risk have shorter stop signal delays (worse) than children at low risk. Boys also have shorter stop signal delays than girls.

```{r sst_ssd_risk_PSanova_posthoc, echo=FALSE}
emmeans(sst_ssd_PSmodel, specs = pairwise ~ risk_status_mom)
emmeans(sst_ssd_PSmodel, specs = pairwise ~ PS)
emmeans(sst_ssd_PSmodel, specs = pairwise ~ sex)
```

\FloatBarrier
\clearpage

## N-back

### Ballanced Accuracy

\FloatBarrier

```{r nback_balacc_risk_anova, echo=FALSE, results='asis'}
kable(anova2dataframe(nback_balacc_anova), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Risk Status x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

```{r nback_balacc_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
nback_balacc_plot
```

Interaction between risk and load shows that children at high familial risk for obesity perform worse at the highest working memory load compared to children at low risk.

```{r nback_balacc_risk_anova_posthoc, echo=FALSE}
emmeans(nback_balacc_mod, specs = pairwise ~ block, adjust = 'fdr')
emmeans(nback_balacc_mod, specs = pairwise ~ block:risk_status_mom, adjust = 'fdr')
```

\FloatBarrier
\clearpage

### d'

\FloatBarrier

```{r nback_dprime_risk_anova, echo=FALSE, results='asis'}
kable(anova2dataframe(nback_dprime_anova), "latex",  digits = 3, caption = 'Nback Balanced Accuracy - Risk Status x Load', booktabs=TRUE) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header"))
```

```{r nback_dprime_risk_fig, echo=FALSE, includ = TRUE, fig.height = 4, fig.width = 6}
nback_drime_plot
```

Interaction between risk and load shows that children at high familial risk for obesity perform worse at the highest working memory load compared to children at low risk.

```{r nback_dprime_risk_anova_posthoc, echo=FALSE}
emmeans(nback_dprime_mod, specs = pairwise ~ block:risk_status_mom, adjust = 'fdr')
emmeans(nback_dprime_mod, specs = pairwise ~ block, adjust = 'fdr')
```

\FloatBarrier
\clearpage
